---
title: "Quick Start with CDER"
author: "Michael Koohafkan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick Start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE
)
```

The R package `cder` provides a simple interface to the CDEC
Webservice. Getting CDEC data with `cder` is easy, just pass a 
station code to `query_cdec`:

```{r}
library(cder)
# get data for CDEC station NSL 
query_cdec("NSL")
```

The CDEC web service uses some default values for the duration code,
sensor number, and start/end dates. You can also specify these 
yourself:

```{r}
station = "NSL"
duration = "event"
sensor = 100 # electrical conductivity
start.date = Sys.Date() - 14
end.date = Sys.Date()

query_cdec(station, sensor, duration, start.date, end.date)
```

The web service supports multiple stations, sensors, and even 
duration codes:

```{r}
# get data for CDEC stations NSL and HUN
stations = c("NSL", "HUN")
# get electrical conductivity and stage
sensors = c(100, 1)
# get event data and hourly averages (where available)
durations = c("event", "hourly")

query_cdec(stations, sensors, durations)
```

That's it! The CDEC Webservice currently does not support querying station
metadata. To browse station data, use the 
[Station Search tool](https://cdec.water.ca.gov/dynamicapp/staSearch)
or [Locator Map](http://cdec.water.ca.gov/cdecstation2/).
