---
title: "Quick Start with CDER"
author: "Michael Koohafkan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick Start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE
)
```

The R package `cder` provides a simple interface to the CDEC
Webservice. Getting CDEC data with `cder` is easy, just pass a 
station code to `cdec_query()`:

```{r eval=FALSE}
# get data for CDEC station NSL
cdec_query("NSL")
```

The CDEC web service uses some default values for the duration code,
sensor number, and start/end dates. However, these default values vary
from station to station, and sometimes a station will return no data by
default. It's generally a good idea to specify these yourself:

```{r}
station = "NSL"
duration = "event" # or "E"
sensor = 100 # electrical conductivity
start.date = "2023-01-01"
end.date = "2023-01-05"

cdec_query(station, sensor, duration, start.date, end.date)
```

The web service supports multiple stations and sensors:

```{r}
# get data for CDEC stations NSL and HUN
stations = c("NSL", "HUN")
# get electrical conductivity and stage
sensors = c(100, 1)
start.date = "2023-01-01"
end.date = "2023-01-05"

cdec_query(stations, sensors, "hourly", start.date, end.date)
```

That's it! The CDEC Webservice currently does not support querying 
station metadata. To browse station data, use the 
[Station Search tool](`r stations_url`)
or [Locator Map](`r map_url`). These
URLs can also be accessed by calling `cdec_search_stations()` and 
`cdec_map()`, respectively. See `help("cdec-search")` for more 
information.To access the metadata page for a particular station, use
`cdec_meta()`.
