---
title: "Quick Start with CDER"
author: "Michael Koohafkan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick Start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE
)
```

The R package `cder` provides a simple interface to the CDEC
Webservice. Getting CDEC data with `cder` is easy, just pass a 
station code to `cdec_query()`:

```{r eval=FALSE}
# get data for CDEC station NSL
cdec_query("NSL")
```

The CDEC web service uses some default values for the duration code,
sensor number, and start/end dates. However, these default values vary
from station to station, and sometimes a station will return no data by
default. It's generally a good idea to specify these yourself:

```{r}
station = "NSL"
duration = "event" # or "E"
sensor = 100 # electrical conductivity
start.date = "2023-01-01"
end.date = "2023-01-05"

cdec_query(station, sensor, duration, start.date, end.date)
```

The web service supports multiple stations and sensors:

```{r}
# get data for CDEC stations NSL and HUN
stations = c("NSL", "HUN")
# get electrical conductivity and stage
sensors = c(100, 1)
start.date = "2023-01-01"
end.date = "2023-01-05"

cdec_query(stations, sensors, "hourly", start.date, end.date)
```

Certain CDEC stations may store non-numeric data flags in the Value
column instead of in the DataFlag column, resulting in parsing issues.
For example, flow data at SGN (Sugar Creek near Callahan) will
sometimes use the codes "ART" and "BRT" to signify discharge at stages
above or below the available rating table. `cder` reexports 
`readr::problems()` to allow you to view these parsing problems, and
additionally writes the problematic rows to a temporary file to
facilitate further investigation.

```{r}
sgn = cdec_query('SGN', 20, start.date = "2022-07-02",
  end.date = "2022-07-03")
problems()
```

That's it! The CDEC Webservice currently does not support querying 
station metadata. To browse station data, use the 
[Station Search tool](`r stations_url`)
or [Locator Map](`r map_url`). These
URLs can also be accessed by calling `cdec_search_stations()` and 
`cdec_map()`, respectively. See `help("cdec-search")` for more 
information.To access the metadata page for a particular station, use
`cdec_meta()`.
