---
title: "Getting started with cder"
output: html_document
---

The R package `cder` provides a simple interface to the CDEC JSON 
Webservice. 


```{r}
library(cder)
```

Getting CDEC data with `cder` is easy. Just pass a station code
to `query_cdec`:

```{r}
# get data for CDEC station NSL 
query_cdec("NSL", sensor, duration, start.date, end.date)
```

The CDEC web service uses some default values for the duration code,
sensor number, and start/end dates. You can also specify these in 
the call to `query_cdec`:

```{r}
station = "NSL"
duration = "event"
sensor = 100 # electrical conductivity
start.date = Sys.Date() - 14
end.date = Sys.Date()

query_cdec(station, sensor, duration, start.date, end.date)
```

The web service supports multiple stations, sensors, and even 
duration codes:

```{r}
# get data for CDEC stations NSL and HUN
stations = c("NSL", "HUN")
# get electrical conductivity and stage
sensors = c(100, 1)
# get event data and hourly averages (where available)
durations = c("event", "hourly")

query_cdec(stations, sensors, durations)
```

That's it!
